### 2017-01-26 papers.tex
Adds new paper

>>>>

% =============================================================================
\section{\texttt{IND\_007} - Educational data mining: A survey from 1995 to
2005}

Paper is~\cite{ind_007}. This is an overview of~\gls{edm}.

Starts by comparing e-learning Data Mining to e-commerce. States that the
differences are as follows:

\begin{itemize}
    \item Domain: E-commerce's purpose is to guide clients in purchasing.
        E-learning's purpose is to guide students in learning.
    \item Data: E-learning has more data then logs, because we have student's
        information.
    \item Objective: The objective of e-commerce is to maximise profit. In
        e-learning is to improve learning, which is more subjective.
    \item Technique: Techniques are different.
\end{itemize}

EDM may be oriented towards different actors who take different points of view
and interest from the analysis. Those actors are:

\begin{itemize}
    \item Students, who want to improve their studying method.
    \item Educators, who want feedback on their education methods, and who want
        to classify students or group their needs and other features.
    \item Oriented towards academics responsible and administrators, who want
        to optimize site performance, among other indicators.
\end{itemize}

The paper lists types of e-learning systems~(\gls{lms}) and how their logs are
made. Also states a few limitations on those logs.

The paper lists data pre-processing tasks and techniques that will also be
useful.

% =============================================================================
\section{\texttt{IND\_008} - Educational Data Mining: A Review of the State of
the Art}

Paper is~\cite{ind_008}.

This paper is a very useful overview of the~\gls{edm} field. It goes on to
explain several points about this field.

The paper asserts that instrumental educational software and databases
containing student information provide big repositories of data which can be
studied to obtain meaning from them. Those studies are made using Statistical
Analysis and Data Mining methods.

EDM has emerged from the need to implement Data Mining methods over these
repositories of data. \gls{edm} as now been subdivided into three areas:

\begin{itemize}
    \item Offline education
    \item E-Learning and~\gls{lms}
    \item Intelligent tutoring systems (ITS) and Adaptive Educational
        Hypermedia Systems (AEHS)
\end{itemize}

An important point is that some pre-processing method and some post-processing
methods for data visualization are not necessarily~\gls{dm} topics, but are
closely related, therefore, they are mentioned in this paper. The mentioned
techniques for pre and post-processing are relevant in the~\gls{edm} field.

The following is a list of Stakeholders of~\gls{edm} projects. It is very
important that this is listed in the final thesis text because it provides the
whole motivation for having done a project like this in the first place.

\begin{itemize}
    \item Learners/Students
    \item Educators/Teachers
    \item Course Developers/Educational Researchers
    \item Learning Providers/Universities
    \item School Administrators and similar
\end{itemize}

For Learners. The results of can be used to recommend activities to students
and suggest interesting learning experiments which are alternative to the
experiences of a particular student. These results can also be used to
recommend interesting courses or point to useful discussions.

For Educators. The results may be used to get objective feedback about
instruction and analyse students. It becomes possible to do the following:

\begin{itemize}
    \item Find common mistakes in students
    \item Predict student grades based on student activities
    \item Determine effective activities
\end{itemize}

For Course Developers. Evaluating the effectiveness of a particular course, how
it is structured, what activities are the most useful and effective, are
important points to take into account when making changes to a course.

For Learning Providers. These are the entities that actually provide the means
to implement learning. These are, for example, Universities, both public and
private, and similar learning institutions.~\gls{edm} can give a powerful
overview of what is the most cost-effective way of assuring good grades,
retention of student, and addition of students who will do well in university.

For School Administrators.~\gls{edm} can give insight on the best ways to
organize human and material resources. In the context of this
project,~\gls{edm} is useful to evaluate the effectiveness of~\gls{edm}.

The paper states that publications in~\gls{edm} have grown a lot and gives some
number for it. There are also a list of publication that are considered to be
extremely relevant.
